Exploratory Data Analysis for College Scorecard Dataset

### 2017-02-23 Draft-xuezhou-sjb.Rmd
update conclusion

When it comes to relationship between control of institution and earning, private for-profit institutions whose predominant degree awarded is graduate degree has the lowest average earnings with the minimum average value at $3100. Public institutions whose predominant degree awarded is graduate degree has the highest average earning with the maximum average value at $45850. Although the graduate degree awarded by public colleges shows the least frequency, it contains the most value because those students (working and not enrolled 6 years after entry) graduating from public colleges holding the graduate degree show the highest average earnings compared with students holding other degrees awarded by different institutions.Also, students graduate from Private Nonprofit institution generally has a higher earning than those students graduate from other types of institutions.

>>>>

When it comes to relationship between control of institution and earning, although the ‘Graduate-degree’ awarded by public colleges and private nonprofit colleges shows a lower frequency, they contain the most value because those students (working and not enrolled 6 years after entry) graduating from public colleges and private nonprofit colleges holding the graduate degree show the highest average earnings compared with students holding other degrees awarded by different institutions. Also, students graduate from Private Nonprofit institution generally has a higher earning than those students graduate from other types of institutions.
